### 2016-04-25 ch03-lrm/truncation.tex
Fix some references

Using convolution, the noiseless output signal in \figref{fig:nparam:trunc:oe} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. 
As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\omega_k)U_0(k)+T_G(\omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\omega_k)$ is the transfer function and $T_G(\omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}

@@

The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:trunc:oe}):
\begin{assumption}
The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:trunc:oe} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.

>>>>

Using convolution, the noiseless output signal in \figref{fig:nparam:blockH0} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. 
As shown in \citet{Pintelon2012} and \citet{Pintelon1997ARB} the \gls{DFT} spectra of the sampled signals at the frequency $\omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\omega_k)U_0(k)+T_G(\omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\omega_k)$ is the transfer function and $T_G(\omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as~\citep{Oppenheim1983}

@@

The following assumptions are consistent with \citep{Schoukens2009LPM} for an \gls{OE} setup (\figref{fig:nparam:blockH0}):
\begin{assumption}
The \gls{SISO} system $G_0$ and  the transients leakage spectrum $T_G$ are both smooth functions of the frequency.
\end{assumption}

@@

% The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{fig:nparam:blockH0} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
% \begin{equation}\label{lpm1spectra}
% Y(k)=G_0(\omega_k)U_0(k)+T(\omega_k)+V_0(k)
% \end{equation}
% where $V_0(k) = H_0(\omega_k)E(k)$ is a noise term, and $T(\omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\omega_k) = T_G(\omega_k) + T_H(\omega_k)$.

### 2016-04-25 ch04-lrmhinf/lrmhinf.tex
Fix some references

\begin{remark}
The optimization problems \eqref{eq:lrmhinf:gammaInxterpolOptim} and \eqref{eq:lrmhinf:gamma-inter-grid} each amount to one-dimensional optimization problems, hence they can be solved accurately, fast and easily by gridding the frequency $\omega$.
The peak amplitudes obtained using both implementations are identical since the local models $\LocalModel[k]{\Delta}$ are evaluated over identical frequency ranges
 \begin{equation}
  \Omega_k 
     = 
       \Set{
           \omega 
           | 
               \leftAdjacent(\omega) = k 
               \vee 
               \rightAdjacent(\omega) = k
      }
 \end{equation}
for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
In \figref{fig:lrmhinf:interpol-quantities} the functions $\leftAdjacent(\omega)$ and $\rightAdjacent(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
\end{remark}

>>>>

\begin{remark}
The optimization problems \eqref{eq:lrmhinf:gammaInterpolOptim} and \eqref{eq:lrmhinf:gamma-inter-grid} each amount to one-dimensional optimization problems, hence they can be solved accurately, fast and easily by gridding the frequency $\omega$.
The peak amplitudes obtained using both implementations are identical since the local models $\LocalModel[k]{\Delta}$ are evaluated over identical frequency ranges
 \begin{equation}
  \Omega_k 
     = 
       \Set{
           \omega 
           | 
               \leftAdjacent(\omega) = k 
               \vee 
               \rightAdjacent(\omega) = k
      }
 \end{equation}
for both methods (but in different order) and aggregated using the supremum operator, which is indifferent to the order of its arguments.
In \figref{fig:lrmhinf:interpol-quantities} the functions $\leftAdjacent(\omega)$ and $\rightAdjacent(\omega)$ are visualized and the equivalence with $\Omega_k$ is apparent.
\end{remark}

### 2016-04-25 ch06-concl/conclusions.tex
Fix some references

As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
There are a few approaches that we think are worthwhile to investigate.
On the one hand, the truncation methods explained in \secref{sec:nparam:trunc} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
On the other hand, one could devise crude model order selection procedures, e.g.  estimating \gls{RFIR} models with increasing complexity until increasing the model order offers no improvement in the non-parametric model.
Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
This doesn't do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.

>>>>

As noted in \remref{rem:initvals:orders:RFIR}, the selection of the model order used in \gls{RFIR} is still an open topic.
There are a few approaches that we think are worthwhile to investigate.
On the one hand, the truncation methods explained in \secref{sec:nonparametric:truncation} could lead to a initial estimate of the impulse response length and hence the required model complexity for \gls{RFIR}.
On the other hand, one could devise crude model order selection procedures, e.g.  estimating \gls{RFIR} models with increasing complexity until increasing the model order offers no improvement in the non-parametric model.
Alternatively, more flexible model structures (e.g. \gls{RARX}) could be tried.
This doesn't do away with the model order selection of the initial model, but it will improve the computational efficiency since less parameters are needed to approximate a particular system.
